Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-11-21 ms.tex
more details on 1/f power spec

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{avg_psd_amp_1.pdf}
\caption{The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
The line shows a 1/f slope law.
}\label{fig:pixelTSeriesPSpec}
\end{figure*}

>>>>

\begin{figure*}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{avg_psd_amp_1.pdf}
\includegraphics[width=.4\columnwidth]{preamp_removed_grp_54.pdf}
\caption{{\it Left:} The average Lomb Scargle periodogram from Amplifier 1's time series over 108 groups.
The noise in the spectrum is close to a 1/f power law (orange line) from 10 to 1000, Hz.
{\it Right:} This 1/f noise introduced in the readout circuit causes prominent correlated noise along the fast-read direction (horizontal).
The amplifier offsets have been removed, but the 1/f noise from these adjacent amplifiers shows different behavior.
}\label{fig:pixelTSeriesPSpec}
\end{figure*}
